The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-11 Article/Article20140406Granada/LatexArt/article_main.tex
Introduction

Algotrading is new, rapidly growing form of trading on financial markets where investor (that makes decisions) is replaced with automaton (computer program) \cite{Leshik2011,Wilinski2014}. Such machine can perform operations (opening and closing positions, placing orders to open positions that meet certain conditions) directly in an automated brokerage platform environment. It may also be a recommendation system that helps investor with making correct decisions.\\

Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets. Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning \cite{Leshik2011,Wilinski,wang,sinclare}. Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis, for example, automatically extracted from the Internet \cite{elder,Wilinski2014,Schwager1996}. Many strategies are based on relatively simple rules. Efficiency of these rules is amplified by using of machine learning \cite{Wilinski,person,tian,krutsinger,lewis,murphy}.\\

Strategy presented in this paper is an example of a solution that can be used fully automated or with investor’s assistance, who makes the decision manually. To use this software, it is necessary to make sure that there are reasonable premises of achieving the success. These conditions can be achieved through inductive thinking \cite{provost,KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future. If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use. If repeated use of said pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational \cite{bishop2006pattern,KleskWilinski}. Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it. Search in the historical patterns, that could be effective in the data space not used for their determination (to identify these patterns), is a major challenge also applied in machine learning which is used in this paper.
The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative, according to the authors, concept of an artificial worm. Subsequently extensive studies of effectiveness of presented strategy in terms of prediction and the aspect of investment are carried out. At the end the conclusions resulting from the study are presented and also cited bibliographic sources are included.

>>>>

Algotrading is a new rapidly growing form of trading on financial markets where investor (that makes decisions) is replaced with trading bot (computer program) \cite{Leshik2011,Wilinski2014}. Such machine can perform operations (opening and closing positions, placing orders to open positions that meet certain conditions) directly in an automated brokerage platform environment. It may also occur as a recommendation system that helps investor with making correct decisions.\\

Such computer applications (bots) require carefully prepared and tested software that most often needs to adapt to the changing situations on the observed markets. Modern trends, in the development of this software, include sophisticated methods of: artificial intelligence, pattern recognition, classification and machine learning \cite{Leshik2011,Wilinski,wang,sinclare}. Those methods are interpenetrating and complementary and are also expanded with information based on fundamental analysis e.g. automatically extracted from the Internet \cite{elder,Wilinski2014,Schwager1996}. Many strategies are based on relatively simple rules. Efficiency of these rules is amplified by using of machine learning \cite{Wilinski,person,tian,krutsinger,lewis,murphy}.\\

Strategy presented in this paper is an example of a solution that can be used fully automatically or with assistance of investor who makes the decision manually. Using such softwaremakes sense only if there are reasonable premises of achieving the success. These conditions can be achieved through inductive thinking \cite{provost,KleskWilinski}, involving the assumption that multiple validation of decision on data from the past substantiates the correctness of the decision in the future. If a certain set of rules in the strategy used to seek the pattern, leads to the success then these rules are a pattern that is encouraged for repeated use. If repeated use of mentioned pattern results in more successes than failures, then the basic premise to consider the use of the pattern is rational \cite{bishop2006pattern,KleskWilinski}. Unfortunately, changing market is causing the pattern to become outdated therefore it is necessary to constantly update it. Finding historically effective patterns that could be also effective in a data space not used for their determination (to identify these patterns) is a major challenge for machine learning which is applied in the paper.
The article is organized as follows: at first authors describe an authored strategy based on an entirely innovative concept of an artificial worm. Subsequently extensive studies of effectiveness of presented strategy in terms of prediction and the aspect of investment are carried out. At the end the conclusions resulting from the study are presented and also cited bibliographic sources are included.
